Generating the Blueprints of the Java Ecosystem

### 2015-02-26 msr.tex
updated msr.tex

In this paper we present: a) the construction process to obtain the collection of the metrics results that the three aforementioned tools produced for {\bf 22730 {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.

@@

The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}. Initially, a snapshot of the Maven repository was downloaded locally. The repository contains various projects and their releases. A project version can be uniquely identified by the following triplet: {\it group id}, {\it artifact id} and {\it version}. The Maven repository contains several versions of each project. All versions were filtered out and only the latest was kept. Each project consists of two {\sc jar} files, one that contains a compiled version of the project and one with the source code. The

>>>>

In this paper we present: a) the construction process to obtain the collection of the metrics results that the three aforementioned tools produced for {\bf 22730} {\sc jar}s, b) our dataset and c) how researchers and practitioners can use the dataset and produce meaningful results.

@@

The dataset construction process is illustrated in Figure~\ref{fig:dataset-construction}. Initially, a snapshot of the Maven repository was downloaded locally. The repository contains various projects and their releases. We identified only the Java projects. The repository contains several versions of each project. All versions were filtered out and only the latest was kept. Each project consists of two {\sc jar} files, one that contains a compiled version of the project and one with the source code. We
